Adopting agile in the large: motivations, success factors and challenges

### 2014-05-14 journal/article.tex
Large organization issues

@@

% The software produced in a large organization may have size and complexity that
% agile struggles to handle.

The primary studies revealed challenges on two areas which relate particularly
to large scale. First, a large software development endeavour must handle
integrating the work products of many teams. Second, a large organization will
have management challenges not seen on small scale.

%% ?? -->
% Include this ???
% Large organization put agile methods under the test of scaling up, and problems
% were encountered.
% In the agile model it was hard for managers to get an overview of the progress
% of the release [P17]. The status of features was hard to tell because different
% aspects of features were sepatated across teams [P17].
% One case reported use of agile across hundreds of teams, but management could
% not get a roll up of the progress without having strict rules on how status was
% reported [P48]. Schnitter and Mackert [P45] report that a maximum workable size
% in a project managed by Scrum was 130 people including 7 development teams.
% % Smits and Rilliet [P48] report that providing executive overview of the
% % development programs was limited by the tools used to manage agile projects.

% Challenge: Previous organization in silos is haunting new model
% Is this good??

In some cases problems were caused by internal boundaries or silos in the
initial organization. Cloke [P10] describes how use of Scrum revealed an
internal segmentation where teams operated with differing priorities and
agendas. This segmentation also hampered the initial effort to use Scrum in a
larger context [P10].
Projects needed specialized skills that were scarce and people were often
relocated to match the needs of the moment, but too much reorganization made
it diffucult for teams to plan ahead [P11].
A dispersed matrix organization causes also problems when people are on one hand
kept assigned to many projects simultaneously, but on the other hand functions
such as database administration, architecture boards, and project management are
centralized [P14].

@@

In a large environment many agile teams coexist and it is possible that their
agile models and vocabularies start diverging. When many teams implement agile
without consistent guidance friction and fragmentation may be generated [P9].
The organization may require moving people between teams from time to time, and
therefore it would be desirable that no big differences in teams' agile cultures
exist. Divergence in process would create risk increasing costs when relocating
people [P38]. Further, if processes of teams diverged management had
difficulties in forecasting and comparing work of different teams [P38, P48].
To overcome problems with divergence in agile models some organizations defined
standards to follow [P8, P43].

A common problem in the agile implementations was the role of managers.
Especially the role of middle management was seen as unclear in agile
methods, but a cultural change would still be required on that level [P2].
It was described that people in management positions needed to resist the
tendency to take command and control to allow room for self-organization, but
the change in role was difficult to achieve for the people involved [P11, P52].
Nielsen and McMunn [P30] describe how the project management group had
previously worked through big up front plans and competing of resources, but
those ways would need to dramatically change.

% Roles of managers (continued)

Several other problems related to management roles were also presented. For
instance, Spayd [P49] describes how managers were left outside the roles offered
by the new agile model. In another case when Scrum masters were appointed from
the ranks of managers developers felt being micromanaged because of vague
understanding of the agile method [P27]. It was also described how mixing the
role of project manager and Scrum master created a conflict in interest, and
turned the Scrum manager's role into one of policing the team instead of
supporting the team [P30]. In some cases problems with manager positions were
solved by phasing out roles relating to the old model, and replacing them with
new positions more suitable for agile [P38, P52].

In most cases a large organizational transformation proceeded gradually, and
during the process it was possible that the new agile model was used in parallel
with the old methods. The arrangement of using the old and new models side by
side was seen as problematic [P1, P26], and causing tensions on all organizational
levels [P10]. Ongoing projects had been set up with previous development
methods, and the agile methods needed to be arranged to fit with them [P8, P29].
A particular problem in sychronizing work between projects using different
models was that in Scrum the software design was fleshed out over time as
sprints progressed, but the waterfall model would require detailed design to be
locked early in the project [P29].

@@

% This where?
Some cases reported that development efforts were controlled on a top level by a
project management office (PMO). The PMO was described as entrenched in a
waterfall paradigm, and the top-level rigidity was causing friction in the
agile adoption [P3, P6]. The PMO was seen as a hub and bottleneck controlling
all aspects of projects, and its central structure had to be dismantled for
the organization to become agile [P46].

>>>>

\subsection{Things that may need to be explained}

* Scrum

* XP

* Definition of sprint

* Self organization and independence of teams -- This is a question relating how
  to organize management.

@@

The primary studies revealed challenges which relate particularly to large
scale. Additional layers of management are usually necessary to steer large
groups of people, but agile methods provide little guidance on how to organize
management. Also, as large organizations accomodate many development teams
problems with synchronizing the development models of teams may cause problems.

The existence of additional management positions may be problematic with agile
processes as they emphasize self organization.
The role of middle management was seen as unclear in agile methods [P2]. This is
problematic as an agile transformation requires cultural change especially on
the middle management level [P2].
It was described that people in management positions needed to resist the
tendency to take command and control to allow room for self organization, but
the change in role was difficult to achieve for the people involved [P11, P52].
Nielsen and McMunn [P30] describe how the project management group had
previously worked through big up front plans and competing of resources, but
those ways would need to dramatically change.

Several other problems related to management roles were also presented. For
instance, Spayd [P49] describes how managers were left outside the roles offered
by the new agile model. In another case when managers were appointed as Scrum
masters developers felt being micromanaged [P27]. This was partially because of
vague understanding of the agile method [P27]. It was also described how mixing
the role of project manager and Scrum master created a conflict in interest, and
turned the Scrum manager's role into one of policing the team instead of
supporting the team [P30]. In some cases problems with manager positions were
solved by phasing out roles relating to the old model, and replacing them with
new positions more suitable for agile [P38, P52].

In most cases a large organizational transformation proceeded gradually, and
during the process it was possible that the new agile model was used in parallel
with the old methods. The arrangement of using the old and new models side by
side was seen as problematic [P1, P26], and causing tensions on all
organizational levels [P10]. Ongoing projects had been set up with previous
development methods, and the agile methods needed to be arranged to fit with
them [P8, P29]. A particular problem in collaborating between projects using
different models was that in Scrum the software design was fleshed out over time
as sprints progressed, but the waterfall model would require detailed design to
be locked early in the project [P29].

Some cases reported that development efforts were still controlled on a top
level by a project management office (PMO). The PMO was described as entrenched
in a waterfall paradigm, and the top-level rigidity was causing friction in the
agile adoption [P3, P6]. The PMO was seen as a hub and bottleneck controlling
all aspects of projects, and its central structure had to be dismantled for the
organization to become agile [P46].

@@

In addition to teams using agile and waterfall methods side by side it is
possible in a large organization that the agile interpretations of teams start
diverging. When many teams implement agile without consistent guidance friction
and fragmentation may be generated [P9]. The organization may require moving
people between teams from time to time, and therefore it would be desirable that
no big differences in teams' agile cultures exist. Divergence in process would
create risk increasing costs when relocating people [P38].
Further, if processes of teams diverged management had difficulties in
forecasting and comparing work of different teams [P38, P48]. To overcome
problems with divergence in agile models some organizations defined standards to
follow [P8, P43].

% Challenge: Previous organization in silos is haunting new model
% Is this good??
In some cases the initial organization had internal boundaries or specialized
knowledge was stuck silos. Such settings caused problems in the agile
implementation.
Cloke [P10] describes how use of Scrum revealed an internal segmentation where
teams operated with differing priorities and agendas. This segmentation also
hampered the initial effort to use Scrum in a larger context [P10].
Cowan [P11] describes how projects needed specialized skills that were scarce
and people were often relocated to match the needs of the moment. Too much
reorganization made it diffucult for teams to plan ahead [P11].

%% This??
% A dispersed matrix organization causes problems when people are on one hand
% kept assigned to many projects simultaneously, but on the other hand functions
% such as database administration, architecture boards, and project management are
% centralized [P14].

%% ?? -->
% Large organization put agile methods under the test of scaling up, and problems
% were encountered.
% In the agile model it was hard for managers to get an overview of the progress
% of the release [P17]. The status of features was hard to tell because different
% aspects of features were sepatated across teams [P17].
%
% One case reported use of agile across hundreds of teams, but management could
% not get a roll up of the progress without having strict rules on how status was
% reported [P48]. Schnitter and Mackert [P45] report that a maximum workable size
% in a project managed by Scrum was 130 people including 7 development teams.
% Smits and Rilliet [P48] report that providing executive overview of the
% development programs was limited by the tools used to manage agile projects.

% --

@@
